### 2022-09-14 dissertation/chapters/01-introduction.tex
🗑️ (dissertation): Removing artifacts

\chapter{Introduction}
\label{chap:introduction}

\begin{quote}
      \textit{The Cephalopod retreats and crawls back up against the glass of the fish tank
            evaluating the situation in front of him. In front of him is a glass jar with
            prey inside. The lid is shut tightly. Never before has he encountered such an
            obstacle in nature, prohibiting him from feeding. He curiously swims closer,
            feeling the shape of the jar with his tentacles. He wraps his tentacles over the
            jar and with a small turn and pop, he releases the lid. The experiment is
            repeated and without hesitation, without failure, he opens the jar, faster, more
            efficiently, every time.}
\end{quote}

@@

@@

This dissertation focuses on the development of a \ac{HH} to train \acp{FFNN} in a
supervised learning approach.

>>>>

\chapter{Introduction}\label{chap:introduction}

\begin{quotation}
      \textit{``It is better to solve one problem five different ways, than to solve five problems one way.'' - George Polya}
\end{quotation}

@@

This dissertation focuses on the development of a specific type of heuristic, called a \acl{HH} to train \acp{FFNN} in a supervised learning approach. In particular, this chapter provides the reader with a brief overview of the problem domain and outlines the research problem, objectives and purpose.

The remainder of the chapter is presented as follows:

\begin{itemize}
      \item \textbf{Section \ref{sec:introduction:summary_problem_domain}} provides the reader with brief summary of the problem domain.

      \item \textbf{Section \ref{sec:introduction:problem}} outlines the research problem being addressed in this dissertation.

      \item \textbf{Section \ref{sec:introduction:motivation}} provides motivations as to why this research is important and valuable to the field.

      \item \textbf{Section \ref{sec:introduction:objectives}} presents the reader with research objectives.
      \item
      \item \textbf{Section \ref{sec:introduction:contributions}} outlines the contributions of this research to the field.

      \item Finally, a full dissertation outline is provided in \textbf{Section \ref{sec:introduction:outline}}.
\end{itemize}

\section{Summary of Problem Domain}
\label{sec:introduction:summary_problem_domain}

@@

The following section outlines the research problem that this dissertation aims to focus on and is followed by a discussion as to why this research endevour is important and valuable to the field.
